\begin{sddsprog}{elegant2genesis}
  \item {\bf description:}
  \verb|elegant2genesis| analyzes particle output data from \verb|elegant| and prepares
  a ``beamfile'' for input to GENESIS\cite{GENESIS}, a 3-D time-dependent FEL code by
  S. Reiche.  The beamfile contains slice analysis of the particle data, and may be
  useful in other applications as well.

  \item {\bf examples:}
  \begin{verbatim}
elegant2genesis run.out beamfile.genesis
elegant2genesis run.out beamfile.gen -totalCharge=3e-9 -slices=100
  \end{verbatim}

  \item {\bf synopsis:}
  \begin{verbatim}
elegant2genesis inputfile outputfile
  [-pipe=[in][,out]] [-textOutput]
  [-totalCharge=coulombs | -chargeParameter=name]
  [-wavelength=meters | -slices=integer]
  [-steer] [-removePTails=deltaLimit=value[,fit][,beamOutput=filename]]
  [-reverseOrder] [-localFit]
  \end{verbatim}

  \item {\bf files:}
  \begin{itemize}
    \item {\em inputfile} --- A particle output file from \verb|elegant| or any other program that uses the same column names and units.
    \item {\em outputfile} --- Contains the slice analysis, suitable for use with SDDS-compliant GENESIS.  The columns are as follows:
      \begin{itemize}
        \item \verb|s|, \verb|t| --- Location of slice in the bunch, in meters or seconds, respectively. \verb|s| is defined so that the head of the bunch is a {\em larger} value, contrary to {\tt elegant}'s convention.
        \item \verb|gamma| --- The average value of $\gamma$ for the slice.
        \item \verb|dgamma| --- The standard deviation of $\gamma$ for the slice.
        \item \verb|xemit|, \verb|yemit| --- The normalized slice emittances in the horizontal and vertical plane, respectively.
        \item \verb|xrms|, \verb|yrms| --- The slice rms beam sizes.
        \item \verb|xavg|, \verb|yavg| --- The slice centroid positions.
        \item \verb|pxavg|, \verb|pyavg| --- The slice centroids for x and y slopes.
        \item \verb|alphax|, \verb|alphay| --- The slice values of the Twiss parameter $\alpha$.
        \item \verb|current| --- The slice current.
        \item \verb|wakez| --- Defined for convenience to be 0.  See GENESIS manual for the meaning.
        \item \verb|N| --- The number of particles in the slice.
      \end{itemize}
  \end{itemize}

  \item {\bf switches:}
  \begin{itemize}
    \item \verb|-pipe[=in][,out]| --- The standard SDDS toolkit pipe option.
    \item \verb|-textOutput| --- Requests text output instead of SDDS output, which may be useful for input to non-SDDS-compliant versions of GENESIS.
    \item \verb|-totalCharge=|{\em coulombs} --- Gives the total charge of the beam in Coulombs.
    \item \verb|-chargeParameter=|{\em name} --- Gives the name of a parameter in {\em inputfile} where the total charge in the beam is given.
    \item \verb|-wavelength=|{\em meters} --- This option is misnamed.  It is actually the slice length in meters.
    \item \verb|-slices=|{\em integer} --- The number of analysis slices to use.
    \item \verb|-steer| --- If given, then the transverse centroids for the bulk beam are all set to zero.  The relative centroid offsets of the slices are, of course, unchanged.
    \item \verb|-removePTails=deltaLimit=|{\em value}\verb|[,fit][,beamOutput=|{\em filename}\verb|]| --- Removes the momentum tails from the beam.  \verb|deltaLimit| is the maximum absolute value of $(p-\langle p \rangle)/\langle p \rangle$ that will be accepted.  If \verb|fit| is given, then a linear fit to $p$ as a function of $t$ is performed, and removal is based on the residuals from that fit.  If \verb|beamOutput| is given, then the filtered beam data is written to the named file for review.
    \item \verb|-reverseOrder| --- By default, the data for the head of the beam comes first.  This option causes \verb|elegant2genesis| to put the data for the tail of the beam first.
    \item \verb|-localFit| --- If given, then for each slice a local linear fit is used to remove any momentum chirp prior to computing the momentum spread.  This produces a momentum spread that is more independent of the number of slices.  Should not be used if the FEL cooperation length is greater than the slice length.
  \end{itemize}

  \item {\bf author:} R. Soliday, M. Borland, ANL/APS.
\end{sddsprog}

