\begin{sddsprog}{sddsnormalize}
  \item \textbf{description:} \verb|sddsnormalize| performs various normalizations of column data.
  \item \textbf{examples:}
    \begin{verbatim}
    sddsnormalize data.sdds norm.sdds -columns=mode=spread,column1,column2
    sddsnormalize data.sdds -columns=suffix=Norm,mode=largest,column1 -pipe=out
    \end{verbatim}
  \item \textbf{synopsis:}
    \begin{verbatim}
    sddsnormalize [inputFile] [outputFile] [-pipe[=input][,output]]
      -columns=[mode=mode][,suffix=string][,exclude=wildcardString],columnName[,columnName...]
    \end{verbatim}
  \item \textbf{switches:}
    \begin{itemize}
      \item {\tt -pipe[=input][,output]} --- The standard SDDS Toolkit pipe option.
      \item {\tt -columns=[mode={\em mode}][,suffix={\em string}][,exclude={\em wildcardString}],columnName[,columnName...]} ---
        Any number of these options may be given. Each specifies columns to normalize and in what {\em mode}. {\em mode} may be
        one of {\tt minimum}, {\tt maximum}, {\tt largest}, {\tt signedLargest}, or {\tt spread}, referring to the factor used for normalization.
        {\tt largest} (the default) is the maximum absolute value; {\tt signedLargest} is the same value but with the sign restored;
        {\tt spread} is the maximum minus the minimum. Each {\em columnName} qualifier gives a possibly wildcarded string specifying
        columns to normalize. {\tt exclude} may be used to exclude columns from normalization that are matched by a {\em columnName}.
        The {\tt suffix} qualifier optionally specifies a suffix to be appended to each column name, to create a new column for the output file; if not given, then the original data are replaced with the normalized data.
    \end{itemize}
  \item \textbf{files:} \emph{inputFile} is an SDDS file containing data to be processed. The \emph{outputFile} argument is optional. If it is not given, and if an output pipe is not selected, then the input file will be replaced.
  \item \textbf{see also:} \progref{sddsprocess}
  \item \textbf{author:} M. Borland, ANL/APS.
\end{sddsprog}
