\begin{sddsprog}{sddsmatrix2column}
  \item \textbf{description:} \verb|sddsmatrix2column| transfers a matrix into a single-column SDDS file.
  \item \textbf{examples:}
    \begin{verbatim}
    sddsmatrix2column matrix.sdds column.sdds
    sddsmatrix2column matrix.sdds column.sdds -rowNameColumn=Label -dataColumnName=Value -rootnameColumnName=ID -majorOrder=row
    \end{verbatim}
  \item \textbf{synopsis:}
    \begin{verbatim}
    sddsmatrix2column [inputfile] [outputfile] [-pipe=[input][,output]]
      [-rowNameColumn=string] [-dataColumnName=string]
      [-rootnameColumnName=string] [-majorOrder=row|column]
    \end{verbatim}
  \item \textbf{files:}
    \begin{itemize}
      \item {\em inputfile} Contains an optional string column and multiple numerical columns. If the string column or \verb|-rowNameColumn| is not provided, Row$<$row\_index$>$ will be used as row names in the output file.
      \item {\em outputfile} Contains two columns: a string column and a data column. The string column combines the input string column (or Row$<$row\_index$>$) and the input data column names.
    \end{itemize}
  \item \textbf{switches:}
    \begin{itemize}
      \item \verb|-pipe=[input][,output]| --- Standard SDDS pipe option for reading/writing from stdin/stdout.
      \item \verb|-rowNameColumn=<string>| --- Column name for row names in the input file. If not provided, Row$<$row\_index$>$ will be used.
      \item \verb|-dataColumnName=<string>| --- Column name of the data column in the output file. Defaults to \verb|Rootname|.
      \item \verb|-rootnameColumnName=<string>| --- Column name of the string column in the output file.
      \item \verb+-majorOrder=row|column+ --- Specifies the binary SDDS layout.
    \end{itemize}
  \item \textbf{see also:} \progref{sddsarray2column}
  \item \textbf{author:} H. Shang, R. Soliday, ANL/APS.
\end{sddsprog}

