\begin{sddsprog}{sddscollapse}
  \item \textbf{description:} \verb|sddscollapse| reads data pages from an SDDS file and writes a new SDDS file containing a single data page. This data page contains only the values of the parameters from the original file, with each parameter forming a column of the tabular data. In spite of the simplicity of the command line, this is an extremely useful program. A typical use might involve processing a multipage file using \verb|sddsprocess| to, for example, obtain statistical analyses of columns for each page; the results of such analyses are placed in parameters. Using \verb|sddscollapse| on this file would produce columns of statistical analyses, with one row for each page. One might then further analyze the data using \verb|sddsprocess|. One could also use \verb|sddscombine| to combine several collapsed, processed data sets into a single file, which puts one formally back in the same position as when one started. In this fashion, multi-level data analysis and collation is possible. This is done with some magnetic measurements at APS.

  \item \textbf{examples:}
  \begin{verbatim}
  sddscollapse APS.twi APS.parameters
  sddscollapse APS.twi -pipe=out | sddspfit -pipe=in fit.sdds -column=nux,nuy -verbose
  \end{verbatim}

  \item \textbf{synopsis:}
  \begin{verbatim}
  sddscollapse [inputFile] [outputFile] [-pipe[=input][,output]]
  \end{verbatim}

  \item \textbf{files:} \verb|inputFile| is the name of an SDDS data set to be collapsed.  \verb|outputFile| is the result.  Note that \verb|outputFile| will not contain any information on the arrays or columns that are in \verb|inputFile|.

  \item \textbf{switches:}
  \begin{itemize}
    \item \verb|-pipe[=input][,output]| --- The standard SDDS Toolkit pipe option.
    \item \verb|-noWarnings| --- Suppresses warnings about file overwrites.
  \end{itemize}

  \item \textbf{see also:}
  \begin{itemize}
    \item \hyperref[exampleData]{Data for Examples}
    \item \progref{sddsprocess}
    \item \progref{sddscombine}
    \item \progref{sddsexpand}
  \end{itemize}

  \item \textbf{author:} M. Borland, ANL/APS.
\end{sddsprog}

