\begin{sddsprog}{sddssequence}
  \item \textbf{description:} \verb|sddssequence| generates an SDDS file with a single page and several columns of data of arithmetic sequences. An example application is generating values for an independent variable that may be used by \progref{sddsprocess} to produce a mathematical function.
  \item \textbf{examples:}
    \begin{verbatim}
    sddssequence example.sdds -define=Index,type=long -sequence=begin=1,number=100,delta=1
    \end{verbatim}
  \item \textbf{synopsis:}
    \begin{verbatim}
    sddssequence [-pipe=[output]] [<outputfile>]
                 -define=<columnName>[,<definitionEntries>] [-repeat=<number>]
                 -sequence=begin=<value>[,number=<integer>][,end=<value>][,delta=<value>][,interval=<integer>]
                 [-sequence=begin=<value>[,number=<integer>][,end=<value>][,delta=<value>][,interval=<integer>] ...]
    \end{verbatim}
  \item \textbf{switches:}
    \begin{itemize}
      \item \verb|-pipe=[output]| --- The standard SDDS Toolkit pipe option.
      \item \verb|-define=<columnName>[,<definitionEntries>]| --- Defines a new column. One or more \verb|-sequence| options should follow. Definition entries have the form \verb|fieldName=value| where \verb|fieldName| is the name of any namelist command field (except the name field) for a column. The default data type is double. To get a different type, use \verb|type=<typeName>|. Multiple \verb|-define| options can be used to create multiple columns, each with its own set of \verb|-sequence| options.
      \item \verb|-sequence=begin=<value>[,number=<integer>][,end=<value>][,delta=<value>][,interval=<integer>]| --- Defines the arithmetic sequence for the data column. More than one \verb|-sequence| option can be given for a column definition, allowing arithmetic sequences of different character in one column. The \verb|begin| value must be given in the first \verb|-sequence| option. If subsequent \verb|-sequence| options follow immediately, a default value equal to the previous \verb|end| value plus the previous \verb|delta| value is used. For the rest of the suboptions, the user must supply \verb|(end,delta)|, \verb|(end,number)|, or \verb|(delta,number)|. If \verb|number| isn't supplied, then the set of \verb|begin|, \verb|end|, \verb|delta| must imply a positive number of rows. The \verb|interval| field specifies the number of rows for which the value is frozen within the sequence.
      \item \verb|-repeat=<number>| --- Repeats the sequence identically for the given number of times.
    \end{itemize}
  \item \textbf{files:} \verb|outputfile| is the name of the SDDS file containing data generated.
  \item \textbf{see also:}
    \begin{itemize}
      \item \progref{sddsprocess}
      \item \progref{sddsprintout}
    \end{itemize}
  \item \textbf{author:} M. Borland, ANL/APS.
\end{sddsprog}
