%\begin{latexonly}
\newpage
%\end{latexonly}
\subsection{sddssort}
\label{sddssort}

\begin{sddsprog}{sddssort}
  \item \textbf{description:} \verb|sddssort| sorts the tabular data section of a data set by the values in named columns.
    Any number of columns may be involved in the sort, and sorting order may be individually specified.
  \item \textbf{examples:}
    \begin{verbatim}
    sddssort APS.twi APS.twi.sorted -column=ElementName
    sddssort APS.twi APS.twi.sorted -column=ElementName -unique
    \end{verbatim}
  \item \textbf{synopsis:}
    \begin{verbatim}
    sddssort [-pipe=[input][,output]] [SDDSinput] [SDDSoutput]
      -column=name[, {increasing | decreasing}] [-column...]
      [-parameter=name[, {increasing | decreasing}] ...]
      [-numericHigh] [-nonDominateSort]
      [-unique[=count]] [-noWarnings]
    \end{verbatim}
  \item \textbf{files:} \emph{SDDSinput} is an SDDS file to be sorted. If it contains multiple data pages, they are treated
    separately. \emph{Warning:} if \emph{SDDSoutput} is not given and \verb|-pipe=output| is not specified, then
    \emph{SDDSinput} will be replaced.
  \item \textbf{switches:}
    \begin{itemize}
      \item \verb|-pipe=[input][,output]| --- The standard SDDS pipe option.
      \item \verb!-column=name[, {increasing | decreasing}]! --- Requests that the column \emph{name} be used to order the rows of each tabular data section. Each subsequent \verb|column| request specifies a subsort of the ordering produced by the previous requests. The \verb|increasing| and \verb|decreasing| keywords may be given to specify the desired ordering of the (sub)sort, with increasing order being the default.
      \item \verb!-parameter=name[, {increasing | decreasing}]! --- Similar to column requests, but sort the data pages by parameters.
      \item \verb|-unique[=count]| --- Specifies that for any rows that are identical in the sort column values, only the first should be included in the output file. If the \verb|count| qualifier is given, then a count of the number of identical rows is supplied in a column called \verb|IdenticalCount|.
      \item \verb|-nonDominateSort| --- Perform non-dominated-sort when multiply sorting columns supplied. Non-dominated-sort only works for numeric columns.
      \item \verb|-numericHigh| --- Works for string sorting which rank the numeric characters higher than other characters in a string comparison. It also ranks numeric character sets with fewer characters below numeric character sets with more characters.
      \item \verb|-noWarnings| --- Suppresses warning messages.
    \end{itemize}
  \item \textbf{see also:} \progref{sddssortcolumn}
  \item \textbf{author:} M. Borland, ANL/APS.
\end{sddsprog}

