\begin{sddsprog}{sddsxref}
  \item \textbf{description:}
  \verb|sddsxref| creates a new data set by adding selected rows from one data set to another.
  Rows are selected by matching string or numeric values in a column present in both input data sets.
  Users may specify which columns of the second data set to take or leave and may transfer
  parameter and array data. \verb|sddsmxref| is a variant that permits multiple \verb|-match|
  and \verb|-equate| options.
  \item \textbf{examples:}
    \begin{verbatim}
sddsxref input.sdds xRef.sdds output.sdds -match=Name -take=Value
sddsxref data.sdds xRef.sdds -equate=Index -reuse=rows -fillIn
    \end{verbatim}
  \item \textbf{synopsis:}
    \begin{verbatim}
sddsxref [-pipe[=input][,output]] [input] [xRefFile] [output]
         [-equate=columnName | -match=columnName]
         [-reuse[=rows][,page]] [-fillIn]
         [-take=columnName,...] [-leave=columnName,...]
         [-transfer={parameter | array},name[,name...]]
         [-ifis={column | parameter | array},name[,name...]]
         [-ifnot={column | parameter | array},name[,name...]]
    \end{verbatim}
  \item \textbf{files:}
    \emph{input} is the data set to which data is being added. \emph{xRefFile} is the data set from
    which data is taken. Warning: if \emph{output} is not given and if \verb|-pipe=out| is not
    specified, \emph{input} is overwritten. For pipe input, the first file listed is taken to be
    \emph{xRefFile}. For pipe input and output, the only file listed is \emph{xRefFile}.
  \item \textbf{switches:}
    \begin{itemize}
      \item \verb|-equate=columnName|, \verb|-match=columnName| --- These options specify the name of a column
        that exists in both \emph{input} and \emph{xRefFile}. For \verb|match| the column must contain
        string data, while for \verb|equate| the column must contain numeric data. For each row in
        \emph{input}, \verb|sddsxref| searches \emph{xRefFile} to find the first row for which the
        \verb|match| column is identical or the \verb|equate| column is equal, as appropriate. If neither
        option is given, rows are taken sequentially from \emph{xRefFile} for each row of \emph{input}.
      \item \verb|-reuse[=rows][,page]| --- By default, each row from \emph{xRefFile} is matched to one row in
        \emph{input}. If \verb|-reuse=rows| is given, each row from \emph{xRefFile} may be matched to any
        number of rows in \emph{input}. Also by default, each page of \emph{input} is matched with the
        corresponding page of \emph{xRefFile}. If \verb|-reuse=page| is given, each page of \emph{input}
        is matched anew to the first page of \emph{xRefFile}. The two qualifiers may be given together.
      \item \verb|-fillIn| --- Normally if there is no match in \emph{xRefFile} for a row in \emph{input},
        that row will not appear in \emph{output}. If \verb|-fillIn| is given, the row will appear, but the
        values for the columns that are being transferred from \emph{xRefFile} will be filled with zeros
        and empty strings, as appropriate.
      \item \verb|-take=columnName,...|, \verb|-leave=columnName,...| --- These options specify which columns
        of \emph{xRefFile} to extract from a matching or equal row for addition to a row of \emph{input}.
        Wildcards may be given in the column names. By default, all columns not in \emph{input} are taken.
        If \verb|take| is employed, only the named columns will be taken. In either case, no column
        specified under \verb|leave| will be taken. \verb|-leave=*| causes no columns to be taken.
      \item \verb!-transfer={parameter | array},name[,name...]! --- This option, which may be given
        multiple times, specifies the names of parameters and arrays to be transferred. Wildcards are not
        presently supported in this option.
      \item \verb!-ifis={column | parameter | array},name[,name...]!, \verb!-ifnot={column | parameter | array},name[,name...]! --- These options allow conditional execution. If any
        column named under \verb|ifis| is not present, execution aborts. If any column named under
        \verb|ifnot| is present, execution aborts.
    \end{itemize}
  \item \textbf{see also:}
    \begin{itemize}
      \item \hyperref[exampleData]{Data for Examples}
      \item \progref{sddsselect}
      \item \progref{sddsmxref}
    \end{itemize}
  \item \textbf{author:} M. Borland, L. Emery, H. Shang, R. Soliday ANL/APS.
\end{sddsprog}
