%\begin{latexonly} 
\newpage 
%\end{latexonly} 
\subsection{sddssinefit} 
\label{sddssinefit} 
 
\begin{itemize} 
\item {\bf description:} \hspace*{1mm}\\ 
{\tt sddssinefit} does a fit to the form:\\
y = $<$constant$>$ + $<$factor$>$ * sin(2*PI*$<$freq$>$*x+$<$phase$>$)
\item {\bf examples:} 
\begin{flushleft}
{\tt sddssinefit <inputfile> <outputfile> -columns=x,y }
\end{flushleft} 
\item {\bf synopsis:}  
\begin{flushleft}
{\tt 
sddssinefit [{\em inputfile}] [{\em outputfile}] [-pipe=[input][,output]] \\ \
{}[-fulloutput] \\ \
{}[-columns={\em x-name},{\em y-name}] \\ \
{}[-tolerance={\em value}] \\ \
{}[-limits=[evaluations={\em number}][,passes={\em number}]] \\ \
{}[-verbosity={\em integer}] \\ \
{}[-guess=[constant={\em constant}][,factor={\em factor}][,frequency={\em freq}][,phase={\em phase}]] \\ \
{}[-majorOrder=row|column]}
\end{flushleft} 
\item {\bf files:} 
The input file contains both the independent and dependent columns {\tt {\em y-name}} and {\tt {\em y-name}}. The output file contains the independent column along with fitted column {\tt {\em y-name}} and {\tt {\em y-name}Fit}.
\item {\bf switches:} 
    \begin{itemize} 
    \item {\tt -fulloutput} --- Includes {\tt {\em y-name}} and {\tt {\em y-name}Residual} in the output file.
    \item {\tt -columns={\em x-name},{\em y-name}} --- The independent and dependent columns.
    \item {\tt -tolerance={\em value}} --- Desired tolerance of simplex minimization. Negative values are\\
                                           fractional, positive numbers are absolute. Default: 1e-6.
    \item {\tt -limits=[evaluations={\em number}][,passes={\em number}]} --- Evaluations and passes for\\
                                                                             simplex minimization. Default: evaluations=100, passes=5.
    \item {\tt -verbosity={\em integer}} --- Increases verbose messages. Valid values are 0-4.
    \item {\tt -guess=[constant={\em constant}][,factor={\em factor}]}\\
          {\tt [,frequency={\em freq}][,phase={\em phase}]} --- Initial guesses for simplex minimization.
    \item {\tt -majorOrder=row|column} --- Specifies the binary SDDS layout.
\end{itemize} 

\item {\bf author:} C. Saunders, M. Borland, R. Soliday, L. Emery, H. Shang, ANL/APS. 
\end{itemize} 
 
