%\begin{latexonly}
\newpage
%\end{latexonly}
\subsection{sddsselect}
\label{sddsselect}

\begin{sddsprog}{sddsselect}
  \item \textbf{description:} \verb|sddsselect| excludes or includes rows from one file based on the presence of matching data in another file. It is similar to \verb|sddsxref|, but unlike that program does not import data from the second file. \verb|sddsmselect| is a variant that permits multiple \verb|-match| and \verb|-equate| options for more sophisticated cross-referencing, but \verb|sddsselect| is faster for single-criterion matching or equating.
  \item \textbf{examples:}
    \begin{verbatim}
    sddsselect APS.twi quadNames.sdds APSquad.twi -match=ElementName -reuse
    sddsselect APS.twi quadNames.sdds APSnquad.twi -match=ElementName -reuse -invert
    \end{verbatim}
  \item \textbf{synopsis:}
    \begin{verbatim}
    sddsselect [-pipe[=input][,output]] [input1] input2 [output] {-match=columnName1[=columnName2] |
      -equate=columnName1[=columnName2]} [-invert] [-reuse[=page][,rows]] [-noWarnings]
    \end{verbatim}
  \item \textbf{files:} \emph{input1} is an SDDS file from which rows of data will be selected for inclusion in \emph{output}. If \emph{input1} contains multiple pages, they are processed separately. \emph{input2} is an SDDS file containing rows of data to use in selecting data from \emph{input1}. \emph{Warning:} if \emph{output} is not given and \verb|-pipe=output| is not specified, then \emph{input1} will be replaced.
  \item \textbf{switches:}
    \begin{itemize}
      \item \verb|-pipe[=input][,output]| --- The standard SDDS Toolkit pipe option.
      \item \verb|-match=columnName1[=columnName2]| --- Specifies the names of string columns from \emph{input1} and \emph{input2} to compare. If \emph{columnName2} is not given, it is taken to be the same as \emph{columnName1}. Data in \emph{columnName1} is taken from \emph{input1} and \emph{columnName2} from \emph{input2}. For each row in a page of \emph{input1}, a match for the string in \emph{columnName1} is sought in any row of \emph{columnName2}. If a match is found, the row is accepted.
      \item \verb|-equate=columnName1[=columnName2]| --- Identical to \verb|-match|, except the columns contain numerical data.
      \item \verb|-invert| --- Specifies that only rows that have no match or equal should be selected for output.
      \item \verb|-reuse[=rows][,page]| --- By default, if \emph{input1} contains multiple pages, each is selected against the corresponding page of \emph{input2}. In addition, each row of \emph{input2} is matched or equated to only one row of \emph{input1}. If \verb|-reuse=page| is given, then each page of \emph{input1} is selected against the first page of \emph{input2}. If \verb|-reuse=rows| is given, each row of \emph{input2} can select any number of rows of \emph{input1}.
      \item \verb|-noWarnings| --- Specifies that no warning messages (about, e.g., file length mismatches or file overwrites) should be issued.
    \end{itemize}
  \item \textbf{see also:} \progref{sddsxref} \progref{sddsmselect}
  \item \textbf{author:} M. Borland, H. Shang and R. Soliday, ANL/APS.
\end{sddsprog}

