\begin{sddsprog}{sddscliptails}
  \item \textbf{description:}
  \verb|sddscliptails| removes the tails from functions, where a tail is a dubious feature
  extending to the left or right of a peak.
  \item \textbf{examples:}
  Remove tails from profiles of beam spots after baseline removal and prior to determining
  rms spot properties. This command clips the tails when the function falls to 1\% of
  its peak value.
  \begin{verbatim}
sddscliptails input.sdds output.sdds -columns=VideoLine* -fractional=0.01
  \end{verbatim}
  \item \textbf{synopsis:}
  \begin{verbatim}
sddscliptails [input] [output] [-pipe=[in][,out]]
  [-columns=listOfNames] [-fractional=value] [-absolute=value] [-fwhm=multiplier]
  [-afterzero[=bufferWidth]]
  \end{verbatim}
  \item \textbf{files:}
  {\em input} is an SDDS file containing one or more pages of data to be processed.
  {\em output} is an SDDS file in which the result is placed. The output file will
  generally have fewer rows than the input file, corresponding to the number of
  rows clipped.
  \item \textbf{switches:}
    \begin{itemize}
    \item {\tt -pipe=[input][,output]} --- The standard SDDS Toolkit pipe option.
    \item {\tt -columns={\em listOfNames}} --- Specifies an optionally-wildcarded list
      of names of columns from which to remove tails.
    \item {\tt -fractional={\em value}} --- Clip a tail if it falls below this fraction of the peak
      value of the column.
    \item {\tt -absolute={\em value}} --- Clip a tail if it falls below this absolute value. This
      value might correspond, say, to a known noise level.
    \item {\tt -fwhm={\em multiplier}} --- Clip a tail if it is beyond {\em multiplier} times
      the full-width-at-half-maximum (FWHM) from the peak of the column.
    \item {\tt -afterzero[={\em bufferWidth}]} --- Clip a tail if it is separated from the
      peak by values equal to zero.
      If {\em bufferWidth} is specified, then a region {\em bufferWidth} wide is kept
      on either side of the peak, if possible.
    \end{itemize}
  \item \textbf{see also:}
    \begin{itemize}
    \item \progref{sddsbaseline}
    \end{itemize}
  \item \textbf{author:} M. Borland, ANL/APS.
\end{sddsprog}

