\begin{sddsprog}{sddshist2d}
  \item \textbf{description:} \verb|sddshist2d| makes two-dimensional histograms of data, producing
    output that is suitable for plotting with \verb|sddscontour|. The two-dimensional histogram
    may include data from two columns, or may show the histograms of a single column versus
    page number.
  \item \textbf{examples:}
    \begin{verbatim}
    sddshist2d par.bpm par.bpm.h2d -column=P1P1x,P1P2x -xparam=50 -yparam=50
    sddscontour -shade=32 par.bpm.h2d -quantity=frequency
    \end{verbatim}
  \item \textbf{synopsis:}
    \begin{verbatim}
    sddshist2d [-pipe[=input][,output]] [inputfile] [outputfile]
      -columns={xName,yName | yName}
      [-weights=columnName[,average]]
      [-xParameters=bins[,lower[,upper]]] [-yParameters=bins[,lower[,upper]]]
      [-outputName=string]
      [-sameScale] [-combine] [-normalize[=sum]] [-smooth[=passes]]
      [-verbose]
    \end{verbatim}
  \item \textbf{switches:}
    \begin{itemize}
      \item \verb|-pipe[=input][,output]| --- The standard SDDS Toolkit pipe option.
      \item \verb!-columns={xName,yName | yName}! --- Specifies the data from the input to histogram. If both
        {\em xName} and {\em yName} are given, then \verb|sddshist2d| does a two-dimensional histogram of the values in
        the named columns. If only {\em yName} is given, then \verb|sddshist2d| does a series of one-dimensional histograms
        of the named column, one for each data page; these histograms are then assembled as a two-dimensional histogram
        with one axis being the page number.
      \item \verb|-weights=columnName[,average]| --- Specifies the name of a column of data with which to proportionally
        weight the count value of points in the histogram. If the \verb|average| qualifier is given, then each bin value
        is normalized to contain the average value of the weight for all points in the bin.
      \item \verb|-xParameters=bins[,lower[,upper]]| --- Specifies the number of bins and optionally the histogrammed region
        for the x values. Ignored if only {\em yName} is given. By default, 21 bins are used encompassing all of the data points.
      \item \verb|-yParameters=bins[,lower[,upper]]| --- Specifies the number of bins and optionally the histogrammed region
        for the y values. By default, 21 bins are used encompassing all of the data points.
      \item \verb|-outputName=string| --- Specifies the name of the histogram data. The default is \verb|frequency|.
      \item \verb|-sameScale| --- Specifies that for multipage input files, the histogram region should be the same for all pages.
        The region is set to encompass all data points from all pages.
      \item \verb|-combine| --- Specifies that for multipage input files, the data from all pages should be placed in a single histogram.
      \item \verb|-normalize[=sum]| --- Specifies normalization of the histogram. If the \verb|sum| qualifier is not given,
        the histogram is normalized to unit amplitude; otherwise, it is normalized so that the sum of all frequencies is unity.
      \item \verb|-smooth[=passes]| --- Specifies smoothing by nearest-neighbor-averaging. If {\em passes} is omitted, only one pass is performed.
      \item \verb|-verbose| --- Requests informational output during processing.
    \end{itemize}
  \item \textbf{see also:}
    \begin{itemize}
      \item \progref{sddshist}
      \item \progref{sddscontour}
      \item \progref{sddscongen}
    \end{itemize}
  \item \textbf{author:} M. Borland, ANL/APS.
\end{sddsprog}

