\begin{sddsprog}{sddsmatrixmult}
  \item \textbf{description:} \verb|sddsmatrixmult| multiplies the matrices represented in two input files and puts the results in the output file. String columns are ignored and not copied to the output file.
  \item \textbf{examples:} In an accelerator beamline a linear relationship exists between the corrector dipole setpoints and the beam position monitor (BPM) readbacks. The matrix data in file \verb|response| is multiplied with the columns of file \verb|correctorChange| to produce \verb|bpmExpectedChange|.
    \begin{verbatim}
sddsmatrixmult response correctorChange bpmExpectedChange
    \end{verbatim}
  \item \textbf{synopsis:}
    \begin{verbatim}
sddsmatrixmult [-pipe=[input][,output]] [file1] file2 [output] [-commute] [-reuse] [-verbose] [-ascii]
    \end{verbatim}
  \item \textbf{files:} The first file (\emph{file1}) is the SDDS file for the left-hand matrix of the product. The second file (\emph{file2}) is the SDDS file for the right-hand matrix. The third file contains the product matrix data.
  \item \textbf{switches:}
    \begin{itemize}
      \item \verb|-pipe[=input][,output]| --- The standard SDDS Toolkit pipe option.
      \item \verb|-commute| --- Use \emph{file1} for the right-hand matrix and \emph{file2} for the left-hand matrix. Useful with \verb|-pipe|.
      \item \verb|-reuse| --- If one file runs out of data pages, reuse the last one.
      \item \verb|-ascii| --- Produce output in ASCII mode. Default is binary.
      \item \verb|-verbose| --- Write diagnostic messages to stderr.
    \end{itemize}
  \item \textbf{see also:} \progref{sddsmatrixop}
  \item \textbf{author:} L. Emery, ANL/APS.
\end{sddsprog}

