\begin{sddsprog}{sddsregroup}
  \item \textbf{description:}
  \verb|sddsregroup| swaps the row indexing and page indexing of data
  in an SDDS file. That is, the ${\rm i^{th}}$ row of all data pages in the input file are collected
  and made into the ${\rm i^{th}}$ data page of the output file.

  \item \textbf{examples:}
  The file \verb|bpm.sdds| contains the beam position monitor (BPM) readback as a function of time for a series
  of consecutive BPMs in a beamline. The defined columns are \verb|Time| and \verb|x|. The parameter
  is \verb|bpmIndex|. The file is regrouped to produce data sets of \verb|x| vs \verb|bpmIndex|
  for each time value. The output is suitable to plot as a movie with \verb|sddsplot|.
  \begin{verbatim}
  sddsregroup bpm.sdds bpm.movie -newParameters=Time -newColumns=bpmIndex
  \end{verbatim}

  \item \textbf{synopsis:}
  \begin{verbatim}
  sddsregroup [-pipe=[input][,output]] inputFile outputFile
    [-newParameters=oldColumnName,...]
    [-newColumns=oldParameterName,...] [-warning] [-verbose]
  \end{verbatim}

  \item \textbf{switches:}
  \begin{itemize}
    \item \verb|-pipe[=input][,output]| --- The standard SDDS Toolkit pipe option.
    \item \verb|-newParameters=oldColumnName,...| --- Specifies columns of the input file that become parameters in the output file. By default no new parameters are created.
    \item \verb|-newColumns=oldParameterName,...| --- Specifies parameters of the input file that become columns in the output file. These columns are duplicated in all pages. By default parameter values are discarded.
    \item \verb|-warning| --- Report non-fatal warnings.
    \item \verb|-verbose| --- Print processing information.
  \end{itemize}

  \item \textbf{files:}
  \begin{itemize}
    \item \verb|inputFile| --- SDDS file containing the data sets to be regrouped.
    \item \verb|outputFile| --- SDDS file containing the regrouped data. If only one file is specified, the input file is overwritten.
  \end{itemize}

  \item \textbf{see also:} \progref{sddsplot}

  \item \textbf{author:} L. Emery, ANL/APS.
\end{sddsprog}

