\begin{sddsprog}{sddsdigfilter}
  \item \textbf{description:}
    \verb|sddsdigfilter| performs time-domain digital filtering of columns of data. Filters can be combined in series and/or
    cascade to produce complex filter characteristics. In addition to allowing simple 1-pole lowpass and highpass filters,
    filter characteristics can be defined using either digital \verb|Z| or analog \verb|S| domain transfer functions.

    A digital filter has a Z transform given by
    \[
    \frac{b_0 + b_1 z^{-1} + \ldots + b_n z^{-n}}{a_0 + a_1 z^{-1} + \ldots + a_n z^{-n}},
    \]
    while an analog filter has a Laplace transform given by
    \[
    \frac{d_0 + d_1 s^{1} + \ldots + d_n s^{n}}{c_0 + c_1 s^{1} + \ldots + c_n s^{n}},
    \]
  \item \textbf{examples:}
    These examples assume the existence of a file \verb|data.wf| containing a waveform stored as a column \verb|value| that is a
    function of a column \verb|time| with units of seconds.
    \begin{verbatim}
    sddsdigfilter data.wf -col=time,value result.wf -low=1,0.01
    sddsdigfilter data.wf -col=time,value result.wf -low=1,10 -high=1,100
    sddsdigfilter data.wf -col=time,value result.wf -low=1,100 -cascade -high=1,10
    sddsdigfilter data.wf -col=time,value result.wf -analog=D,1.0,0.01,C,0.1,0.3,1.6
    sddsdigfilter data.wf -col=time,value result.wf -digital=B,0,0,0,0,0,1
    \end{verbatim}
  \item \textbf{synopsis:}
    \begin{verbatim}
    sddsdigfilter [inputFile] [outputFile] [-pipe=[input][,output]]
      -columns=xName,yName
      [-proportional=gain]
      [-lowpass=gain,cutoffFrequency]
      [-highpass=gain,cutoffFrequency]
      [-digitalfilter=sddsfile,aCoeffName,bCoeffName]
      [-digitalfilter=[A,a0,a1,..,am][,B,b0,b1,..,bn]]
      [-analogfilter=sddsfile,cCoeffName,dCoeffName]
      [-analogfilter=[C,c0,c1,..,cm][,D,d0,d1,..,dn]]
      [-cascade]
      [-verbose]
    \end{verbatim}
  \item \textbf{files:}
    Two file names are required: the name of the existing input file and the name of the output file to be produced. The input
    file must contain at least two columns: one containing the data to be filtered ({\em yName}) and the other giving time
    information ({\em xName}). A linear time scale is assumed for {\em xName}. The output file is a copy of the input file with
    an additional column called {\tt DigFiltered}{\em yName} where {\em yName} would be the name of the original y-column.
  \item \textbf{switches:}
    \begin{itemize}
      \item {\tt -pipe[=input][,output]} --- The standard SDDS Toolkit pipe switch.
      \item {\tt -columns={\em xName},{\em yName}} --- The names of the input file data columns.
      \item {\tt -proportional={\em gain}} --- Defines a gain stage, where {\em gain} is the multiplier applied to the data.
      \item {\tt -lowpass={\em gain},{\em cutoffFrequency}} --- Defines a lowpass filter stage, where {\em gain} is the
        multiplier applied to the data and {\em cutoffFrequency} is the -3dB point of the filter in units appropriate to the
        supplied {\em xName}.
      \item {\tt -highpass={\em gain},{\em cutoffFrequency}} --- Defines a highpass filter stage, where {\em gain} is the
        multiplier applied to the data and {\em cutoffFrequency} is the -3dB point of the filter in units appropriate to the
        supplied {\em xName}.
      \item {\tt -digitalfilter={\em sddsfile},{\em aCoeffName},{\em bCoeffName}} --- Defines a digital filter with
        coefficients in the supplied SDDS coefficient file. This file must contain two columns containing the A and B
        coefficients of a digital \verb|Z| transfer function. Control theory convention assumes that the A0 coefficient is
        always 1.0. To ensure consistency with the SDDS file, the a0 coefficient is the first row in the A-column and must be
        implicitly supplied. Although there is little benefit to setting a0 to anything other than 1.0, it is allowed.
      \item {\tt -digitalfilter=[A,{\em a0},{\em a1},...,{\em am}][,B,{\em b0},{\em b1},...,{\em bn}]} --- Defines a digital
        filter with the A and B coefficients of the digital \verb|Z| transfer function supplied on the command line. Either A or
        B or both coefficients can be supplied. If no A coefficients are supplied, a0 is set to 1.0. Equally, if no B
        coefficients are supplied, b0 is set to 1.0. If different numbers of A and B coefficients are supplied, the filter order
        is determined from the largest order.
      \item {\tt -analogfilter={\em sddsfile},{\em cCoeffName},{\em dCoeffName}} --- Defines an analog filter with
        coefficients in the supplied SDDS coefficient file. This file must contain two columns containing the C and D
        coefficients of an analog \verb|S| transfer function. Conversion to the digital domain is done using a bilinear
        transform. Note that the user must ensure adequate data sampling, since the general format does not allow frequency
        warping based on the filter cutoff frequency.
      \item {\tt -analogfilter=[C,{\em c0},{\em c1},...,{\em cm}][,D,{\em d0},{\em d1},...,{\em dn}]} --- Defines an analog
        filter with the C and D coefficients of the analog \verb|S| transfer function supplied on the command line. Either C or
        D or both coefficients can be supplied. If no C coefficients are supplied, then c0 is set to 1.0. Equally, if no D
        coefficients are supplied, then d0 is set to 1.0. Conversion to the digital domain is done using a bilinear transform.
        Note that the user must ensure adequate data sampling, since the general format does not allow frequency warping based on
        the filter cutoff frequency.
      \item {\tt -cascade} --- Defines the start of a new filter stage. Any number of filter stages can be supplied for a single
        data set. If more than one filter is defined, then the outputs are summed unless the {\tt -cascade} switch is supplied
        between the filter definitions, in which case the output of the first filter stage is fed into the input of the
        subsequent filter stage.
      \item {\tt -verbose} --- Prints the filter coefficients for each filter stage.
    \end{itemize}
  \item \textbf{author:} John Carwardine, ANL/APS.
\end{sddsprog}

