\begin{sddsprog}{sddscollect}
  \item \textbf{description:}
    \verb|sddscollect| reorganizes tabular data from the input file to bring data from several groups of
    similarly named columns together into a single column per group. In doing so it creates one page
    of output for every row on the input file and creates parameters to hold data from columns that
    are not included in any group.
  \item \textbf{examples:}
    Take a data set with several columns of PAR BPM x and y readings (one set per row) and create a
    new file with one column for x readings and one column for y readings, with each page containing
    one set of readings.
    \begin{verbatim}
sddscollect par.bpm par.orbits -collect=suffix=x -collect=suffix=y
    \end{verbatim}
    The output file has three columns, \verb|x|, \verb|y|, and \verb|Rootname|, the last containing the
    original column names without the suffix.
    Do statistics on PAR BPM x and y readbacks, then collect the statistics into columns, one column
    for each type of statistic:
    \begin{verbatim}
sddsprocess par.bpm -pipe=out -process=P?P?[xy],spread,%sSpread \
  -process=P?P?[xy],ave,%sMean -process=P?P?[xy],stand,%sStDev | sddscollapse | \
sddscollect -pipe=in parbpm.stat \
  -collect=suffix=xSpread -collect=suffix=xMean -collect=suffix=xStDev \
  -collect=suffix=ySpread -collect=suffix=yMean -collect=suffix=yStDev
    \end{verbatim}
    The output file has columns \verb|xSpread|, \verb|ySpread|, \verb|xMean|, \verb|yMean|,
    \verb|xStDev|, and \verb|yStDev|, plus \verb|Rootname| containing the remainder of each original
    column name after the suffix is removed. All collections must produce matching sets of name
    remainders.
  \item \textbf{synopsis:}
    \begin{verbatim}
sddscollect [input] [output] [-pipe[=input][,output]] \
  -collect={suffix|prefix|match}=match[,column=newName][,editCommand=<string>]
    \end{verbatim}
  \item \textbf{switches:}
    \begin{itemize}
      \item \verb|-pipe[=input][,output]| --- The standard SDDS Toolkit pipe option.
      \item \verb!-collect={suffix|prefix|match}=match[,column=newName][,editCommand=<string>]! --- Specifies
        a string, \emph{match}, to look for at the end (suffix mode), beginning (prefix mode), or
        anywhere (match mode) in column names. Data from all matching columns is transferred into a
        single column in the output file. For prefix and suffix modes, the default name of this
        column is the suffix or prefix string, while for match mode it is created by applying the
        edit command to the matching column names. This may be changed with the \verb|column|
        qualifier. All collections must produce the same number of matches and the set of name
        remainders (i.e., the original column name less the prefix or suffix, or following editing)
        must be the same for each collection.
    \end{itemize}
  \item \textbf{files:}
    Input and output are SDDS files. Each output page corresponds to one input row.
  \item \textbf{see also:}
    \begin{itemize}
      \item \progref{sddsregroup}
      \item \progref{sddstranspose}
      \item \progref{sddsEditing}
    \end{itemize}
  \item \textbf{author:} M. Borland, ANL/APS.
\end{sddsprog}

