\begin{sddsprog}{sddsmselect}
  \item \textbf{description:}
    \verb|sddsmselect| selects data from \emph{input1} for writing to \emph{output} based on the presence or absence of matching data in \emph{input2}. If \emph{output} is not given, \emph{input1} is replaced.
  \item \textbf{examples:}
    \begin{verbatim}
sddsmselect <input1> <input2> <output> -match=ControlName
    \end{verbatim}
  \item \textbf{synopsis:}
    \begin{verbatim}
sddsmselect [input1] [input2] [output] [-pipe=[input][,output]] \\
  [-match=column-name[=column-name][,...]] \\
  [-equate=column-name[=column-name][,...]] \\
  [-invert] \\
  [-reuse[=[rows][,page]]] \\
  [-nowarnings] \\
  [-majorOrder=row|column]
    \end{verbatim}
  \item \textbf{switches:}
    \begin{itemize}
      \item \verb|-pipe=[input][,output]| --- Standard SDDS pipe options for reading/writing files from stdin/stdout.
      \item \verb|-match| --- Specifies names of columns to match between \emph{input1} and \emph{input2} for selection and placement of data taken from \emph{input1}.
      \item \verb|-equate| --- Specifies names of columns to equate between \emph{input1} and \emph{input2} for selection and placement of data taken from \emph{input1}.
      \item \verb|-invert| --- Specifies that only non-matched rows are to be kept.
      \item \verb|-reuse| --- Specifies that rows of \emph{input2} may be reused, i.e., matched with more than one row of \emph{input1}. Also, \verb|-reuse=page| specifies that only the first page of \emph{input2} is used.
      \item \verb!-nowarnings! --- Specifies that warning messages should be suppressed.
      \item \verb!-majorOrder=row|column! --- Specifies the binary SDDS layout.
    \end{itemize}
  \item \textbf{files:}
    Input and output are SDDS files.
  \item \textbf{see also:}
    \begin{itemize}
      \item \progref{sddsselect}
    \end{itemize}
  \item \textbf{author:} C. Saunders, M. Borland, R. Soliday, H. Shang, ANL/APS.
\end{sddsprog}

