%
\begin{sddsprog}{sddslorentzianfit}
  \item \textbf{description:}
  Performs a Lorentzian fit to data in an SDDS file, using the model
  $y = \verb|baseline| + \verb|height| \gamma^2/(\gamma^2 + (x - \verb|center|)^2)$.
  \item \textbf{examples:}
    \begin{verbatim}
sddslorentzianfit beam.sdds fit.sdds -columns=Frequency,Signal,ySigma=Error -fitRange=1e3,2e3 -guesses=baseline=0,center=1.5e3,height=10,gamma=50
sddslorentzianfit -pipe=both -columns=x,y -fixValue=gamma=0.05 -verbosity=2 -fullOutput
    \end{verbatim}
  \item \textbf{synopsis:}
    \begin{verbatim}
sddslorentzianfit [inputfile] [outputfile] [-pipe=[input][,output]]
-columns=<x-name>,<y-name>[,ySigma=<sy-name>]
[-fitRange=<lower>|@<parameter-name>,<upper>|@<parameter-name>]
[-fullOutput] [-verbosity=<integer>] [-stepSize=<factor>]
[-tolerance=<value>]
[-guesses=[baseline=<value>|@<parameter-name>][,center=<value>|@<parameter-name>]
         [,height=<value>|@<parameter-name>][,gamma=<value>|@<parameter-name>]]
[-fixValue=[baseline=<value>|@<parameter-name>][,center=<value>|@<parameter-name>]
          [,height=<value>|@<parameter-name>][,gamma=<value>|@<parameter-name>]]
[-limits=[evaluations=<number>][,passes=<number>]] [-majorOrder=<row|column>]
    \end{verbatim}
  \item \textbf{switches:}
    \begin{itemize}
      \item \verb|-pipe=[input][,output]| --- Read/write SDDS data using standard streams.
      \item \verb|-columns=<x-name>,<y-name>[,ySigma=<sy-name>]| --- Specify data and optional error columns.
      \item \verb!-fitRange=<lower>|@<parameter-name>,<upper>|@<parameter-name>! --- Restrict the fit to a data range.
      \item \verb|-fullOutput| --- Include fit and residual columns in the output file.
      \item \verb|-verbosity=<integer>| --- Set diagnostic output level.
      \item \verb|-stepSize=<factor>| --- Specify step-size factor for derivative estimation.
      \item \verb|-tolerance=<value>| --- Set convergence tolerance.
      \item \verb!-guesses=[baseline=<value>|@<parameter-name>][,center=<value>|@<parameter-name>][,height=<value>|@<parameter-name>][,gamma=<value>|@<parameter-name>]! --- Provide starting parameter values.
      \item \verb!-fixValue=[baseline=<value>|@<parameter-name>][,center=<value>|@<parameter-name>][,height=<value>|@<parameter-name>][,gamma=<value>|@<parameter-name>]! --- Fix selected parameters.
      \item \verb|-limits=[evaluations=<number>][,passes=<number>]| --- Limit number of evaluations and passes.
      \item \verb!-majorOrder=<row|column>! --- Choose output data ordering.
    \end{itemize}
  \item \textbf{author:} M. Borland, ANL/APS.
\end{sddsprog}
