\begin{sddsprog}{sddsvslopes}
  \item \textbf{description:}
    \verb|sddsvslopes| makes straight line fits of vectorized data in the input file with respect to a selected parameter used as independent variable. The simplest example of vectorized data is a data set with one parameter and two columns, one string column of rootnames and one numerical column of data. The fitting is looped over rows across all the data sets in the input file using a selected parameter as the independent variable. The output file contains vectorized slope and intercept data for each column specified in the input file.
  \item \textbf{examples:}
    \begin{verbatim}
sddsvslopes corrector.sdds corrector.vslopes -independentVariable=CorrectorSetpoint -columns=x
    \end{verbatim}
  \item \textbf{synopsis:}
    \begin{verbatim}
sddsvslopes [-pipe=[input][,output]] inputFile outputFile
  -independentVariable=parameterName [-columns=listOfNames]
  [-excludeColumns=listOfNames] [-sigma[=generate]] [-verbose]
    \end{verbatim}
  \item \textbf{files:}
  The input file contains the tabular data for fitting. The column \verb|Rootname| must be present. The output file contains one data set of vectorized slope and intercept data. The \verb|Rootname| and \verb|Index| columns from the input file are transferred to the output file. If column \verb|Index| doesn't exist in the input file, then it is created in the output file. The column names are \emph{name}\verb|Slope| and \emph{name}\verb|Intercept| where \emph{name} is the name of the fitted data. If only one file is specified, then the input file is overwritten by the output. A string parameter called \verb|IndependentVariable| is defined containing the name of the independent variable.
  \item \textbf{switches:}
    \begin{itemize}
      \item \verb|-pipe[=input][,output]| --- The standard SDDS Toolkit pipe option.
      \item \verb|-independentVariable=parametername| --- Name of independent variable (default is the first valid column).
      \item \verb|-columns=listOfNames| --- Columns to be individually paired with independentVariable for straight line fitting.
      \item \verb|-excludeColumns=listOfNames| --- Columns to exclude from fitting.
      \item \verb|-sigma[=generate]| --- Calculates errors by interpreting column names \emph{name}\verb|Sigma| or \verb|Sigma|\emph{name} as sigma of column \emph{name}. If these columns don't exist, then the program generates a common sigma from the residual of a first fit and refits with these sigmas. If option \verb|-sigma=generate| is given, then sigmas are generated from the residual of a first fit for all columns, irrespective of the presence of columns \emph{name}\verb|Sigma| or \verb|Sigma|\emph{name}.
      \item \verb|-ascii| --- Make output file in ascii mode (binary is the default).
      \item \verb|-verbose| --- Prints some output to stderr.
    \end{itemize}
  \item \textbf{see also:}
    \begin{itemize}
      \item \progref{sddsprocess}
      \item \progref{sddsrowstats}
    \end{itemize}
  \item \textbf{author:} L. Emery, ANL/APS.
\end{sddsprog}
