\begin{sddsprog}{sddsrowstats}
  \item \textbf{description:}
    \verb|sddsrowstats| analyzes data across columns on a row-by-row basis to
    find minima, maxima, averages, standard deviations, etc. The output is a
    copy of the input with additional columns that contain the desired
    statistics.

  \item \textbf{examples:}
    Find the mean x and y orbits from PAR beam-position-monitor data collected
    with one set of x and y values (in 32 columns) per row.
    \begin{verbatim}
sddsrowstats par.bpm par.bpm1 -mean=xMean,P?P?x -mean=yMean,P?P?y
    \end{verbatim}

  \item \textbf{synopsis:}
    \begin{verbatim}
sddsrowstats [-pipe=[input][,output]] [input] [output]
             [-nowarnings]
             [-mean=newName[,limitOps],columnNameList]
             [-rms=newName[,limitOps],columnNameList]
             [-median=newName[,limitOps],columnNameList]
             [-minimum=newName[,limitOps],columnNameList]
             [-maximum=newName[,limitOps],columnNameList]
             [-standardDeviation=newName[,limitOps],columnNameList]
             [-sigma=newName[,limitOps],columnNameList]
             [-mad=newName[,limitOps],columnNameList]
             [-sum=newName[,limitOps][,power=<integer>],columnNameList]
             [-drange=newName[,limitOps],columnNameList]
             [-qrange=newName[,limitOps],columnNameList]
             [-smallest=newName[,limitOps],columnNameList]
             [-largest=newName[,limitOps],columnNameList]
             [-count=newName[,limitOps],columnNameList]
    \end{verbatim}
    where \emph{columnNameList} is a comma-separated list of one or more
    optionally wildcarded names and \emph{limitOps} is of the form
    \verb|[topLimit=value][,bottomLimit=value]|.

  \item \textbf{switches:}
    \begin{itemize}
      \item \verb|-pipe=[input][,output]| --- The standard SDDS Toolkit pipe
        option.
      \item \verb|-mean|, \verb|-rms|, \verb|median|, \verb|minimum|,
        \verb|maximum|, \verb|standardDeviation|, \verb|sigma|, \verb|mad|,
        \verb|drange|, \verb|qrange|, \verb|smallest|, \verb|largest|,
        \verb|count| --- Compute indicated statistic across the columns
        specified in \emph{columnNameList}. If \emph{limitOps} are given, then
        values above the \verb|topLimit| or below the \verb|bottomLimit| are
        excluded from computations. \verb|sigma| is the standard deviation of
        the mean. \verb|mad| is the mean-absolute-deviation. \verb|smallest|
        (\verb|largest|) is the minimum (maximum) absolute value. \verb|drange|
        and \verb|qrange| are the decile and quartile ranges, respectively.
      \item \verb|-sum=newName[,power=integer],columnNameList| --- Specifies
        creation of a new column \emph{newName} containing the row-by-row sums
        of the columns specified in \emph{columnNameList}. The values are
        summed after being raised to the given power, which is 1 by default.
    \end{itemize}

  \item \textbf{see also:}
    \begin{itemize}
      \item \hyperref[exampleData]{Data for Examples}
      \item \progref{sddschanges}
      \item \progref{sddsenvelope}
      \item \progref{sddsprocess}
    \end{itemize}

  \item \textbf{author:} M. Borland, ANL/APS.
\end{sddsprog}

