%\begin{latexonly}
\newpage
%\end{latexonly}
\subsection{sddsfindin2dgrid}
\label{sddsfindin2dgrid}

\begin{sddsprog}{sddsfindin2dgrid}
  \item \textbf{description:} \verb|sddsfindin2dgrid| searches a two-dimensional grid of data and returns the grid coordinates where two specified columns are closest to requested values. The requested values may be supplied directly with \verb|-atValues| or read from an SDDS file with \verb|-valuesFile|. Optional interpolation refines the location, and \verb|-inverse| performs the reverse operation, interpolating data values from supplied grid coordinates.
  \item \textbf{examples:}
  \begin{verbatim}
  sddsfindin2dgrid data.sdds locations.sdds -gridVariables=x,y -findLocationOf=Fx,Fy -atValues=0.1,0.2 -interpolate
  sddsfindin2dgrid grid.sdds out.sdds -gridVariables=Qx,Qy -findLocationOf=R11,R12 -valuesFile=targets.sdds -mode=reuseFirstPage
  sddsfindin2dgrid grid.sdds values.sdds -gridVariables=x,y -findLocationOf=Fx,Fy -valuesFile=positions.sdds -inverse
  \end{verbatim}
  \item \textbf{synopsis:}
  \begin{verbatim}
  sddsfindin2dgrid [input] [output] [-pipe=[input][,output]]
    -gridVariables=gridColumnName1,gridColumnName2
    -findLocationOf=columnName1,columnName2
    {-valuesFile=filename | -atValues=value1,value2}
    [-presorted] [-interpolate]
    [-mode={onePairPerPage|reuseFirstPage|all}]
    [-inverse]
  \end{verbatim}
  \item \textbf{switches:}
  \begin{itemize}
    \item \verb|-gridVariables=gridColumnName1,gridColumnName2| \textendash{} names of columns giving grid coordinates.
    \item \verb|-findLocationOf=columnName1,columnName2| \textendash{} columns for which to locate or interpolate values.
    \item \verb+{-valuesFile=filename | -atValues=value1,value2}+ \textendash{} supply target pairs directly or from a file.
    \item \verb|-presorted| \textendash{} declare that grid variables are sorted to speed the search.
    \item \verb|-interpolate| \textendash{} interpolate within grid cells for sub-grid accuracy.
    \item \verb+-mode={onePairPerPage|reuseFirstPage|all}+ \textendash{} control how value pairs are used for multipage data.
    \item \verb|-inverse| \textendash{} interpolate data values for supplied grid coordinates.
    \item \verb+-pipe[=input][,output]+ \textendash{} standard SDDS Toolkit pipe option.
  \end{itemize}
  \item \textbf{files:}
  \begin{itemize}
    \item \emph{input} \textendash{} SDDS file containing the grid data.
    \item \emph{output} \textendash{} SDDS file receiving the resulting coordinates or values.
  \end{itemize}
  \item \textbf{see also:}
  \begin{itemize}
    \item \progref{sdds2dinterpolate}
    \item \progref{sddssnap2grid}
  \end{itemize}
  \item \textbf{author:} M. Borland, ANL/APS.
\end{sddsprog}
