\begin{sddsprog}{sddsanalyticsignal}
\item \textbf{description:} \verb|sddsanalyticsignal| computes the analytic signal of selected real data columns using a Hilbert transform.  It outputs the real and imaginary parts as well as the magnitude and phase (both wrapped and unwrapped).
\item \textbf{examples:}
  Compute the analytic signal of column \verb|signal| as a function of \verb|time|:
  \begin{verbatim}
sddsanalyticsignal data.sdds result.sdds -columns=time,signal
  \end{verbatim}
\item \textbf{synopsis:}
  \begin{verbatim}
sddsanalyticsignal [inputfile] [outputfile] [-pipe=[input][,output]] \
  [-columns=indep-variable,depen-quantity[,...]] \
  [-unwrapLimit=value] \
  [-majorOrder=row|column]
  \end{verbatim}
\item \textbf{switches:}
  \begin{itemize}
  \item \verb|-pipe[=input][,output]| --- The standard SDDS Toolkit pipe option.
  \item \verb|-columns=indep-variable,depen-quantity[, ...]| --- Specifies the independent variable and one or more dependent columns to analyze.  Wildcards are permitted for the dependent quantity names.
  \item \verb|-unwrapLimit=value| --- Sets the relative magnitude threshold for phase unwrapping.  Unwrapping is applied only when the signal's magnitude exceeds this fraction of its maximum.
  \item \verb!-majorOrder=row|column! --- Specifies the binary SDDS layout of the output file.
  \end{itemize}
\item \textbf{files:} \emph{inputfile} is an SDDS file containing real data columns.  \emph{outputfile} is an SDDS file that will receive the analytic signal.
\item \textbf{see also:} \progref{sddsfft}.
\item \textbf{author:} H. Shang, R. Soliday, ANL/APS.
\end{sddsprog}
